### 2011-05-27 thesis/abstract.tex
More thesis structure

\chapter*{Resumo}
Let $E$ denote the set of all possible texts in English and $P$ the set of
all possible texts in Portuguese. A transformation $T_{E->P}(x)$ can be defined
in $E \times P$, such that it maps $x \in E$ to a translated version $y \in P$ such
that they hold the same semantic meaning to a reader.

Assume this text to be $T_{E->P}(abstract)$.
\footnote{What I mean is that this will be a translation of the english text present
on abstract and don't expect it to be filled in before the final version of this
document!}

>>>>

% Portuguese Version of the above.
\chapter*{Resumo}
Assume this text to be $T_{E \rightarrow P}(abstract)$.
\footnote{What I mean is that this will be a translation of the English text
present on abstract. Also don't expect it to be filled in before the final
version of this document!}
